Asymmetric Agents and their Willingness to Fight\\ Customer Loyalty and its Impact on Competition

### 2015-10-07 Paper1.tex
text and spelling

Efforts either increase the return per customers or leave it unchanged such that $\gamma_1'(x_1)\geq 0$. Additionally, $\gamma_1''(x_1) - c_1<0$. This implies that efforts don't decrease the valuation of the product and that in lieu of competition the optimal level of efforts is finite.

\subsection{General Case}
The reaction function of firm $1$ to a change in the efforts of firm $2$ is given by:
\begin{align}
\frac{\d x_1}{\d x_2} &= g'(x_1^C-x_2^C)\left(\frac{\d x_1}{\d x_2}-1\right)\frac{\gamma_1}{c_1} + g(x_1-x_2)\left(\frac{\d x_1}{\d x_2}-1\right)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1} + G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{\d x_1}{\d x_2}\frac{\gamma}{c_1}\\
\frac{\d x_1}{\d x_2} &= A_i^{-1} \left(-g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1} - g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\right)\\
A_i &= 1 - g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}-g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{\gamma}{c_1}
\end{align}

Assuming that $A_i>0$, that $\frac{\partial \gamma_1}{\partial x_1}>0$, we find that the sign of the reaction function depends on $g'(\cdot)$. The reaction is positive if $g'(\cdot)$ is sufficiently negative. Then the level of competition increase sufficiently to raise the incentives to compete more. If $g'(\cdot)$ is close to zero, competition intensity does still increase, but is offset by the lower market share. A lower market share makes extracting profits from the customers less valuable, thus making $\frac{\partial \gamma_i}{\partial x_i}$ less important. Thus, for small negative and large positive $g'(\cdot)$ and increase in $x_2$ leads to lower competition and a lower effort by $1$.

\subsection{Without positive effect on revue}
The reaction function of firm $i$ to a change in the efforts of firm $j$ is derived as:
\begin{align}
\frac{\d x_1^C}{\d x_2} &= g'(x_1^C-x_2^C)\gamma_1\left(\frac{\d x_1^C}{\d x_2}-1\right)\\
\frac{\d x_1^C}{\d x_2} &= \frac{-g'(x_1^C-x_2^C)\gamma_1}{1+g'(x_1^C-x_2^C)\gamma_1}
\end{align}
If $g'(x_1^C-x_2^C)<-1$ the market cannot be in equilibrium as an increase in $x_1$ would lead to an even greater increase in $x_1$ already by itself.

>>>>

Efforts either increase the return per customers or leave it unchanged such that $\gamma_1'(\cdot)\geq 0$. Additionally, $\gamma_1''(\cdot) - c_1<0$. This implies that efforts don't decrease the valuation of the product and that in lieu of competition the optimal level of efforts is finite.

\subsection{General Case}
The reaction function of firm $1$ to a change in the efforts of firm $2$ is given by:
\begin{align}
\frac{\d x_1}{\d x_2} &= g'(x_1^C-x_2^C)\left(\frac{\d x_1}{\d x_2}-1\right)\frac{\gamma_1}{c_1} + g(x_1-x_2)\left(\frac{\d x_1}{\d x_2}-1\right)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1} + G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{\d x_1}{\d x_2}\frac{\gamma}{c_1}\\
\frac{\d x_1}{\d x_2} &= A_i^{-1} \left(-g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1} - g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}\right)\\
A_i &= 1 - g'(x_1^C-x_2^C)\frac{\gamma_1}{c_1}-g(x_1-x_2)\frac{\partial \gamma_1}{\partial x_1}\frac{1}{c_1}-G(x_1-x_2)\frac{\partial^2 \gamma_1}{\partial^2 x_1}\frac{\gamma}{c_1}
\end{align}
Assuming that $A_i>0$ and that $\frac{\partial \gamma_1}{\partial x_1}>0$, we find that the sign of the reaction function depends on $g'(\cdot)$. The reaction is positive if $g'(\cdot)$ is sufficiently negative. Then the level of competition increase sufficiently to raise the incentives to compete more intensively. If $g'(\cdot)$ is close to zero, competition intensity does still increase, but is offset by the lower market share. A lower market share makes extracting profits from the customers less valuable, thus making $\frac{\partial \gamma_i}{\partial x_i}$ less important. Thus, for small negative and large positive $g'(\cdot)$ and increase in $x_2$ leads to lower competition and a lower effort by $1$.

\subsection{Without positive effect on revenue}
The reaction function of firm $i$ to a change in the efforts of firm $j$ is derived as:
\begin{align}
\frac{\d x_1^C}{\d x_2} &= g'(x_1^C-x_2^C)\gamma_1\left(\frac{\d x_1^C}{\d x_2}-1\right)\\
\frac{\d x_1^C}{\d x_2} &= \frac{-g'(x_1^C-x_2^C)\gamma_1}{1+g'(x_1^C-x_2^C)\gamma_1}
\end{align}
If $g'(x_1^C-x_2^C)<-1$ the market cannot be in equilibrium as an increase in $x_1$ would lead to an even greater increase in $x_1$ already by itself.
